The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-16 paper/main.tex
paper: caption clarification

\begin{figure}[!tb]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate as a 
        function of planet radius in Model \#3. This model has fixed primaries 
        and 
        single stars, but varying secondaries. The true planet radius 
        distribution is 
        a power law with exponent $-2.92$ above $2r_\oplus$, below which it is 
        uniform 
        \citep[similar to][]{howard_planet_2012}. We use an arbitrary 
        normalization of 
        $Z_0=0.5$ throughout.}
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate as a 
        function of planet radius in a model with a radius gap 
        (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Model \#3, this model has fixed primaries and single stars, 
        but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}

>>>>

\begin{figure}[!tb]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
        bins) as a function of planet radius in Model \#3. This model has 
        fixed primaries 
        and 
        single stars, but varying secondaries. The true planet radius 
        distribution is 
        a power law with exponent $-2.92$ above $2r_\oplus$, below which it is 
        uniform 
        \citep[similar to][]{howard_planet_2012}. We use an arbitrary 
        normalization of 
        $Z_0=0.5$ throughout.}
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
        bins) as a function of planet radius in a model with a radius gap 
        (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Model \#3, this model has fixed primaries and single stars, 
        but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}
